Designing and Developing a Personalised Recommender System

### 2021-01-17 paper/paper.tex
filling out paper with initial thoughts

\subsection{Domain of application}
This application is a hybrid recommender system using the Yelp dataset.

@@

\subsection{Purpose/Aim}
The purpose and aim

@@

\subsection{Data description}
Description of data

\subsection{Data preparation and future selection}
Prepare data

\subsection{Hybrid scheme}
Which two algorithms

\subsection{Recommendation techniques/algorithms}
What techniques

@@

\subsection{Input interface}
What is the input interface

@@

\subsection{Output interface}
What is the output interface

>>>>

\subsection{Domain of application}
The domain of this application is a recommender system for bars, using the Yelp dataset.
Decide whether I want to define the time-span for the date, 
depends on if there is too much data from all available time period.
I am also taking into accounts Covid-19 data when generating recommendations.

@@

\subsection{Purpose/Aim}
The purpose of this application is to give suitable suggestions for a user to go to.
Using information about the user such as their location and personal preferences.

@@

\subsection{Data description}
The data I am using is taken from the Yelp dataset,
it includes user reviews of different businesses and services in a specific location.
These user reviews include ratings, text feedback, and other such information.

\subsection{Data preparation and feature selection}
Prepare data
The entire Yelp dataset is huge and much of it is not neccessary for my domain of bars.
As such I prepared the data by eliminating any data not relevant to my domain.
I selected features such as user ratings and a particular user's average rating,
since if a user typically rates places they go highly, but rates a particular bar low,
this is more significant than a user who always rates places low.

\subsection{Hybrid scheme}
Which two algorithms
A hybrid scheme is a good way to design a recommender system, since you can get the
best of both algorithms if done properly.
Meaning better recommendations than either algorithm could achieve individually.

\subsection{Recommendation techniques/algorithms}
The first recommender system is collaborative filtering.
I am using a weighted mixed combination of these two systems in order to produce the results
of my hybrid recommender system.

@@

\subsection{Input interface}
The input interface is the command line.
The program offers users opportunites to input information about themselves,
as well as make choices from a selection of items which the system provides or suggests.

@@

\subsection{Output interface}
The output interface is the command line.
The system can output recommendations for bars which the user might like,
as well as information about how the system works and why certain suggestions were made,
at the user's request.
